Storing messages with multipartite neural cliques

### 2014-07-03 Articles/article.tex
...
..

	 \begin{abstract}
	 	We extend recently introduced associative memories based on cliques to multipartite cliques. We propose a variant of the classic retrieving rule. We study their relative performance for retrieving partially erased and corrupted messages. We provide both analytical and simulation results showing improvements of capacity over.
	 \end{abstract}

@@

@@

		\subsubsection{The "$a$ winners take all" rule}

@@

@@

	As the probability for $i$ and $j$ to be active in their respective clusters for one message is $\frac{a}{l}$, providing messages are independent, it follows that the probability for the edge $(i,j)$ of not being added in the network for one message is $1 - \left(\frac{a}{l}\right)^2$. Thus the density $d$ can be expressed like this :

@@

	Thanks to the memory effect $\gamma$, activated neurons in a non-erased cluster stays activated and are the only ones doing so in their cluster. For neurons in erased clusters, the maximum attainable score is $a(c - c_e)$. Neurons corresponding to the original message achieve this score. Besides the probability for a neuron $v$ to achieve the maximum score in such a cluster, that is to mean $a(c-c_e)$ is $d^	{a(c-c_e)}$.

	probability for a vertex $v$	not to achieve the maximum : $1 - d^	{a(c-c_e)}$

@@

	\subsubsection{Simulations}
		gap of theoretical density with density in simulations : under $1$ percent

@@

@@

	For errors : only better than only 1 activity per cluster if multiple iterations of the $a$-winners take all rule.
	For one iteration, it is less efficient.
	\begin{figure}
		\includegraphics[width=8.5cm]{Courbes/densiteexemple.pdf}
		\caption{Theoretical and empirical densities}
	\end{figure}

	\begin{figure}
		\includegraphics[width=8.5cm]{Courbes/remplacement_figure2g1} %{comparaison_regles_pool5_a2c4l512e2}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
		\end{figure}

	\newpage
	p
	\newpage

	\subsection{Retrieving corrupted messages}
	\begin{figure}
		\includegraphics[width=8.5cm]{Courbes/remplacement_figure3g1}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, one erroneous cluster, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
	\end{figure}

	Formula for errors instead of erasures :

@@

@@

@@

	$
	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{gc} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
	$

@@

	generalisation to multiple activities per cluster :
	\newpage
	a
	\newpage

@@

	%\begin{align*}
	$P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{bc} < n)^{l-2a} P(n_{abc} < n)^a \right ]^{c_e}
	$
	%\end{align*}

@@

	\newpage
	a
	\newpage

@@

	$P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n = 1}^{a ( c- c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}$	
	\nocite{*}
	\bibliographystyle{numeric} % Le style est mis entre crochets.
         \bibliography{bibli.bib}
\end{document}

>>>>

	 \begin{abstract}
	 	We extend recently introduced associative memories based on clustered cliques to multipartite cliques. We propose a variant of the classic retrieving rule. We study its performance relatively to the former one for retrieving partially erased and corrupted messages. We provide both analytical and simulation results showing improvements in networks capacities.
	 \end{abstract}

@@

	Let $\mathcal{M}$ be a set of messages of length $c$ over the alphabet $\mathcal{A} = \{1, 2, \hdots, {l \choose a}\}$ and $m = | \mathcal{M} |$. Messages in $\mathcal{M}$ are stored in an undirected unweighted graph, or neural network, of $c \cdot l$ vertices or neurons.

	Each message $x = (x_i)_{1 \le i \le c}$ is mapped to $y = (y_i)_{1 \le i \le c}$ where $y_i$ is the binary representation of the $x_i$-th $a$-combination of $l$ elements (the mapping doesn't matter as long as it is fixed).

	Storing a message $x$ in the network amounts to consider the network in state $y$, that is for all $1 \le j \le l$ and $1 \le i \le c$, the neuron $j$ in the cluster $i$ is activated if and only if $y_{i,j} = 1$ ; then adding all connections between activated neurons excepting for neurons sharing the same cluster. Thus we obtain a multipartite clique between activated neurons of message.

@@

		\subsubsection{The "$a$ winners take all" rule}
		$a$-rank

@@

		$w = a$

@@

	As the probability for $i$ and $j$ to be active in their respective clusters for one message is $\frac{a}{l}$ providing messages are independent, it follows that the probability for the edge $(i,j)$ of not being added in the network for one message is $1 - \left(\frac{a}{l}\right)^2$. Thus the density $d$ can be expressed like this :

@@

	Thanks to the memory effect $\gamma$, activated neurons in a non-erased cluster stay activated and are the only ones doing so in their cluster. For neurons in erased clusters, the maximum attainable score is $a(c - c_e)$. Neurons corresponding to the original message achieve this score. Besides the probability for a neuron $v$ to achieve the maximum score in such a cluster, that is to mean $a(c-c_e)$ is $d^	{a(c-c_e)}$.

	%probability for a vertex $v$	not to achieve the maximum : $1 - d^	{a(c-c_e)}$

@@

	\subsubsection{Simulations}
		gap of theoretical density with density in simulations : under $1$ percent, see Figure \ref{densiteth}

@@

	See Figure \ref{erasuresth}

@@

	For errors : only better than only 1 activity per cluster if multiple iterations of the $a$-winners take all rule.
	For one iteration, it is less efficient.
	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/densiteexemple.pdf}
		\caption{Theoretical and empirical densities}
			\label{densiteth}
	\end{figure}

	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/remplacement_figure2g1} %{comparaison_regles_pool5_a2c4l512e2}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, two erasures, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
			\label{erasuresth}
		\end{figure}

	\newpage
	p
	\newpage
	$\,$
	\newpage

	\subsection{Retrieving corrupted messages}

	\subsubsection{Analytical result}	
	Formula for errors instead of erasures :

@@

	Correct neurons in uncorrupted clusters achieve at least a score of $a(c-c_e - 1) + \gamma$.

@@

	Correct neurons in corrupted clusters achieve at least a score of $a(c - c_e)$.

@@

	\begin{align}
	P_{retrieve} = \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{gc} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-1} \right ]^{c - c_e} \\ \times \left [ \sum_{n = 1}^{c-1+\gamma} P(n_{ge} = n) \left [ \sum_{x=0}^{n-1} P(n_{bc} = x) \right]^{l-2} \left [ \sum_{x=0}^{n-1} P(n_{abc} = x) \right] \right ]^{c_e}
	\end{align}

@@

	generalisation to multiple activities per cluster :

@@

	\newpage
	$\,$
	\newpage	
	\begin{align*}
	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
	 &\times \left [ \sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{bc} < n)^{l-2a} P(n_{abc} < n)^a \right ]^{c_e}
	\end{align*}

@@

	See \ref{corruptth}

	\newpage
	$\,$
	\newpage

	\subsubsection{Simulations}
	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/remplacement_figure3g1}
		\caption{2 activities per cluster, 4 clusters, 512 neurons per cluster, one erroneous cluster, each point is the mean of 5 networks with 1000 sampled messages, analytical result in continuous black}
		\label{corruptth}
	\end{figure}

@@

	$P(\mbox{no other vertex activated in any cluster})=  \left ( \sum_{n = 1}^{a ( c- c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] \left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \right)^{c_e}$

	\newpage
	$\,$
	\newpage
	\begin{figure}
		\includegraphics[width=8.5cm]{Courbes/1comppsic4l512g1}
		\caption{Comparison between different number of activities per cluster :  4 clusters, 512 neurons per cluster, 1000 sampled messages}
	\end{figure}

	\nocite{*}
	\bibliographystyle{numeric} % Le style est mis entre crochets.
         \bibliography{bibli.bib}
\end{document}
